Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-05-27 fib2.tex
many minor edits, plus included some R- and F- move diagrams, clarified a few technical points, and made comments on figures

%\usepackage{tikz}
%\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
%\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
%\usepackage{bm}  % Define \bm{} to use bold math fonts

@@

\newcommand{\eps}{\epsilon}

@@

\begin{abstract}
Classically simulating the dynamics of excitations in two-dimensional quantum systems that 
support anyons is likely intractable in general because such dynamics are sufficient for 
universal quantum computation. However, processes of interest for the study of quantum 
error correction in anyon systems are typically drawn from a restricted class that displays 
significant structure over a wide range of system parameters.
We exploit this structure to classically simulate, and thereby demonstrate the success of, an 
error-correction protocol for a quantum memory based on the universal Fibonacci anyon 
model.  We numerically simulate a phenomenological model of the system and noise 
processes on lattice sizes of up to 
$128\times128$ sites, and find a lower bound on the error-correction threshold of 
approximately $12.5\%$, which is comparable to those previously known for abelian and 
(non-universal) nonabelian anyon models.
\end{abstract}

@@

Topologically ordered quantum systems in two dimensions offer tremendous promise for 
long-term storage and processing of quantum information~\cite{Kitaev2003, Dennis2002, Nayak2008}. 
The topological features of such systems are insensitive to local 
perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have excitations 
displaying anyonic statistics~\cite{Wilczek1990}. These anyons can in general be used as 
quantum memories~\cite{Kitaev2003, Dennis2002} or to perform universal topological 
quantum computation~\cite{Freedman2002, Nayak2008}.

Quantum error correction is vital to harnessing the computational power of these topologically 
ordered systems. When coupled to a heat bath at any finite temperature, thermal fluctuations 
will create spurious anyons that diffuse and quickly corrupt the stored quantum 
information~\cite{Pastawski2010}. Thus, the passive protection provided by the mass gap 
at low temperature must be augmented by an \emph{active} decoding procedure.

Decoding algorithms are generally designed to run efficiently, but simulating the physical error-correction procedure also requires simulating the dynamics of the noise and recovery processes. 
Because of this, almost all of the sizable research effort on active quantum error correction for topological systems has focused on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}.
%~\cite{Dennis2002, Duclos-Cianci2010, Bravyi2011, Bravyi2014}.
Systems of abelian anyons are well suited to studying quantum error correction because (at the RG fixed point) noise and recovery processes can be efficiently simulated numerically, allowing lattice simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
Standard algorithms are specifically tailored to exploit the abelian nature of these particles, and specifically that abelian anyons cannot be used for quantum computation.

Recent investigations have begun to explore quantum error correction for nonabelian anyon 
models~\cite{Brell2013, Wootton2013, Hutter2014}. Nonabelian anyon models are particularly interesting 
because braiding and fusion of these anyons in general allows for the implementation of universal quantum 
computation. However, the initial studies of error-correction in nonabelian anyon systems have focused on specific models, such as the Ising 
anyons~\cite{Brell2013} and the so-called $\Phi$-$\Lambda$ 
model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal. The general dynamics of these particular anyon models is known to be classically simulable, a fact
that was exploited to enable efficient simulation of error correction in these systems. When considering more general anyon models, their ability to perform universal quantum computation would seem a significant barrier to their simulation on a classical computer. While simulation of general dynamics does indeed seem intractable, we argue that the kinds of processes that are typical of thermal noise are sufficiently structured to allow for their classical simulation in precisely the regimes where we expect successful error correction to be possible. This insight allows us to simulate both noise and error-correction for a quantum code based on a universal anyon model.

Here we consider a full simulation of quantum error correction in a two-dimensional lattice 
system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum 
computation~\cite{Freedman2002, Nayak2008}. Fibonacci anyons are experimentally motivated as the 
expected excitations of the $\nu=\frac{12}{5}$ fractional quantum Hall 
states~\cite{Slingerland2001}, and can also be realized in several spin 
models~\cite{Levin2005, Bonesteel2012, Kapit2013, Palumbo2014} and composite 
heterostructures~\cite{Mong2014}.

We use a flexible phenomenological model of dynamics and thermal noise to describe a system with Fibonacci anyon excitations. Within this model, we apply existing general topological error-correction protocols to simulate the successful preservation of quantum information encoded in topological degrees of freedom. Topological quantum computation protocols using nonabelian anyons typically implicitly assume the existence of an error-correction protocol to correct for diffusion or unwanted creation of anyons. Our results are the first explicit demonstration that such a scheme will be successful when applied to a universal topological quantum computer.

@@

The fusion outcome of any particular experiment depends on the history of the particles, in 
particular how they have braided around one another. Braiding operations are treated as 
unitary actions on the fusion space. Pair-creation events should be considered isometries 
that enlarge the fusion space, while fusion events correspond to projective measurements 
of combined charge of some number of particles. For details of the description of these 
processes in Fibonacci anyons, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.

We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
microscopic details of the system. 
This is consistent with the principles of topologically 
ordered systems and anyonic physics, where the key universal features describing the 
anyon model correspond to large length-scale physics, while the microscopic physics plays 
a less important (and non-universal) role. Effectively, we simulate a topological quantum field theory on a discrete space-time.
As such, we model the system simply as a 
periodic $L\times L$ square lattice $\Lambda$ of sites upon which sets of anyons can 
reside. Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
locally on edges of $\Lambda$. For more details of an analogous model, see~\cite{Brell2013}.

@@

Our error-correction algorithm is based on a hard-decision renormalization group (RG) 
decoder~\cite{Bravyi2011}. 
The decoder proceeds by measuring the occupations of 
anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons 
within each cluster, before iterating at increasing length scales.
It terminates when the lattice 
is free of anyons (i.e.~we have returned to the codespace) or the decoder performs a homologically nontrivial operation, thereby altering the codespace.
%\cggb{A few more details? What is our length schedule?} 
%\cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} 
Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, although it may not be clear in all cases how to extend these decoders to the non-abelian setting.
The advantage of using a hard-decision RG decoder is 
its simplicity and flexibility, and the fact that its clustering scheme is compatible with the structure in the noise processes that allows us to classically simulate them.

@@

Below the (bond) percolation threshold for (say) a 2D square lattice, we expect random sets of 
bonds to decompose into separate clusters~\footnote{We use the word cluster to refer both to groupings of nearby anyons as formed by the decoding algorithm and to connected components of a graph under percolation, since both of these usages are standard in the literature. The intended meaning will remain clear from context.} of average size $O(\log(n))$ and variance 
$O(1)$~\cite{Bazant2000}.
Each noise process in our model is associated with a (randomly distributed) edge, and so 
disconnected clusters correspond to sets of anyons that could not have interacted at any 
point in their history. As such, we can simulate the braiding processes of each cluster 
separately. In other words: the quantum state in the fusion space of all anyons factorizes into 
a tensor product over bond clusters, and we can compute each factor separately. Since each 
cluster has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. There are rare 
random processes that violate this reasoning, but processes such as these are suppressed 
exponentially in $L$, the lattice size~\cite{Grimmett1989}.

However, random noise processes are not the only dynamics that we need to consider. We 
must also consider the effect of the error-correction routine itself. This acts iteratively to fuse 
particles on increasing length scales. While this kind of fusion would typically merge clusters, 
forcing us to compute dynamics of larger and larger sets of anyons, large clusters are sparse 
(and thus unlikely to be merged), and in addition at each length scale the total number of 
anyons present is dramatically reduced by fusion, leading to a smaller number of anyons that 
must be simulated.

Of course, if we were to consider noise so strong that the clusters percolate over the entire lattice, we would no longer expect to be able to efficiently simulate the system for large $L$. 
However, recall that logical errors in our system correspond to processes that act over a non-trivial loop of the torus. 
Our simulation remains efficient until the point that we start to create nontrivial loops around the torus, and our simulation declares failure at this point, meaning that we can simulate large lattice sizes in this regime, including up to $L=128$.

@@

\begin{figure}[th!]
\begin{center}
	\includegraphics[width=\columnwidth]{pic-syndrome.pdf}
\caption{Four equivalent representations of a state,
along with two syndrome observables marked with solid and dashed lines:
(a) two pairs are joined in (b).
Deform the curve straight to get (c),
then effect some
braid operations on the state so that (d) the two
observables are now represented on the curve.
}
\label{f:syndrome}
\end{center}
\end{figure}

\begin{figure}[th!]
\begin{center}
	\includegraphics[width=\columnwidth]{pic-decode.pdf}
\caption{The decoder works by maintaining a set of disjoint clusters (rooted trees).}
\label{f:decode}
\end{center}
\end{figure}

@@

We can guarantee that error-correction will succeed whenever noise does not percolate, but it is possible that percolated events may still result in no error. 
The connection between the percolation threshold and the error-correction threshold is not well understood in general~\cite{Hastings2014}, though it is clear that our threshold estimate will be a lower bound for the true threshold that may be found if all events (including those that have percolated) were simulated by an optimal decoder. 
However, calculations of such nontrivial operations suggest that all such processes will indeed result in a logical or leakage error.
As such it is likely that neglecting full simulation for such events does not significantly effect our observed threshold value.

@@

We have demonstrated classical simulation of successful error correction in a universal anyon model. 
Though we have chosen several properties of our model and simulation in a convenient way for simplicity, we think it very unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}. 
In particular, although we have modeled our logical qubit as encoded in the global topological degrees of freedom of our system, we could have encoded it in the fusion space of several preferred $\tau$ anyons. 
This situation would be appropriate to model error-correction routines for topological quantum computation. 
Additionally, we expect our results to be stable to changes in details of the noise model, decoding algorithm, and so on.

>>>>

\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit}
\usepackage{epstopdf} % to include .eps graphics files with pdfLaTeX
%\usepackage{bm}  % Define \bm{} to use bold math fonts

@@

\newcommand{\e}{\mathrm{e}}

@@

\begin{abstract}
Classically simulating the dynamics of excitations in two-dimensional quantum systems that 
support anyons is likely intractable in general because such dynamics are sufficient to implement 
universal quantum computation. However, processes of interest for the study of quantum 
error correction in anyon systems are typically drawn from a restricted class that displays 
significant structure over a wide range of system parameters.
We exploit this structure to classically simulate, and thereby demonstrate the success of, an 
error-correction protocol for a quantum memory based on the universal Fibonacci anyon 
model.  We numerically simulate a phenomenological model of the system and noise 
processes on lattice sizes of up to 
$128\times128$ sites, and find a lower bound on the error-correction threshold of 
approximately $12.5\%$, which is comparable to those previously known for abelian and 
(non-universal) nonabelian anyon models.
\end{abstract}

@@

Topologically ordered quantum systems in two dimensions show tremendous promise for 
long-term storage and processing of quantum information~\cite{Kitaev2003, Dennis2002, Nayak2008}. 
The topological features of such systems are insensitive to local 
perturbations~\cite{Bravyi2010, Bravyi2011a, Michalakis2013}, and have quasiparticle excitations 
exhibiting anyonic statistics~\cite{Wilczek1990}. These systems can in general be used as 
quantum memories~\cite{Kitaev2003, Dennis2002} or to perform universal topological 
quantum computation~\cite{Freedman2002, Nayak2008}.

Quantum error correction is vital to harnessing the computational power of topologically 
ordered systems. When coupled to a heat bath at any finite temperature, thermal fluctuations 
will create spurious anyons that diffuse and quickly corrupt the stored quantum 
information~\cite{Pastawski2010}. Thus, the passive protection provided by the mass gap 
at low temperature must be augmented by an \emph{active} decoding procedure.

In order to efficiently classically simulate an error-correction protocol for a topologically ordered quantum memory, it is necessary to simulate the physical noise processes, the decoding algorithm, and the physical recovery operations. Decoding algorithms are typically designed to run efficiently on a classical computer, but there is generally no guarantee that the noise and recovery processes should be classically simulable.
Because of this, almost all of the sizable research effort on active quantum error correction for topological systems has focused on the case of abelian anyons~\cite{Dennis2002, Duclos-Cianci2010, Duclos-Cianci2010a, Wang2010, Wang2010a, Duclos-Cianci2013, Bravyi2011, Bombin2012, Wootton2012, Anwar2014, Watson2014, Hutter2014a, Bravyi2014, Wootton2015, Fowler2015, Andrist2015}.
%~\cite{Dennis2002, Duclos-Cianci2010, Bravyi2011, Bravyi2014}.
Systems of abelian anyons are well suited to studying quantum error correction because (at the RG fixed point) noise and recovery processes can be efficiently simulated numerically, allowing lattice simulations of decoding with over 1 million sites~\cite{Duclos-Cianci2010}. 
Standard algorithms are specifically tailored to exploit the abelian nature of these particles, particularly that abelian anyons cannot be used for quantum computation.

Recent investigations have begun to explore quantum error correction for nonabelian anyon 
models~\cite{Brell2013, Wootton2013, Hutter2014}. Nonabelian anyon models are especially interesting 
because braiding and fusion of these anyons in general allows for the implementation of universal quantum 
computation. However, the initial studies of error-correction in nonabelian anyon systems have focused on specific models, such as the Ising 
anyons~\cite{Brell2013} and the so-called $\Phi$-$\Lambda$ 
model~\cite{Wootton2013, Hutter2014} that, while nonabelian, are not universal. The general dynamics of these particular anyon models is known to be efficiently classically simulable, a fact
that was exploited to enable efficient simulation of error correction in these systems. When considering more general anyon models, their ability to perform universal quantum computation would seem a significant barrier to their simulation on a classical computer. While simulation of general dynamics does indeed seem intractable, we argue that the kinds of processes that are typical of thermal noise are sufficiently structured to allow for their classical simulation in the regimes where we expect successful error correction to be possible. This insight allows us to simulate the noise and recovery processes for a quantum code based on a universal anyon model.

Concretely, we consider the simulation of quantum error correction in a two-dimensional lattice 
system with Fibonacci anyons, a class of nonabelian anyons that are universal for quantum 
computation~\cite{Freedman2002, Nayak2008}. Fibonacci anyons are experimentally motivated as the 
expected excitations of the $\nu=\frac{12}{5}$ fractional quantum Hall 
states~\cite{Slingerland2001}, and can also be realized in several spin 
models~\cite{Levin2005, Bonesteel2012, Kapit2013, Palumbo2014} and composite 
heterostructures~\cite{Mong2014}.

We use a flexible phenomenological model of dynamics and thermal noise to describe a system with Fibonacci anyon excitations. Within this model, we apply existing general topological error-correction protocols, and simulate the successful preservation of quantum information encoded in topological degrees of freedom. Topological quantum computation protocols using nonabelian anyons typically implicitly assume the existence of an error-correction protocol to correct for diffusion or unwanted creation of anyons. Our results are the first explicit demonstration that such a scheme will be successful when applied to a universal topological quantum computer.

@@

The fusion outcome of any particular experiment depends on the history of the particles, in 
particular how they have braided around one another. Braiding operations are treated as 
unitary actions on the fusion space. Pair-creation events should be considered isometries 
that enlarge the fusion space, while fusion events correspond to projective measurements 
of combined charge of some number of particles. For detailed description of these 
processes in Fibonacci anyons, see e.g.~Ref.~\cite{Nayak2008} and references therein. 
Braiding of Fibonacci anyons and measurements of fusion outcomes is known to be 
sufficient to implement universal quantum computation~\cite{Freedman2002, Nayak2008}.

The dynamics and history of a system of anyons can be conveniently represented by a graphical calculus, which can be regarded as a representation of the world-lines of the particles. These diagrams can be manipulated by $R$-moves, corresponding to braiding processes:
	\begin{align}
		\begin{tikzpicture}[baseline=0.5cm,scale=0.33]		
			\draw(0,0)--(0,1);
			\draw plot [smooth, tension=1] coordinates { (0,1) (0.75,1.8) (-0.6,2.45) (-1,3)};
			\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
			\draw plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
			\node at (0,0) [anchor=north] {$c$};
			\node at (-1,3) [anchor=south] {$b$};
			\node at (1,3) [anchor=south] {$a$};
		\end{tikzpicture}
		&\;\;=\;\;R^{ab}_c\cdot\;
		\begin{tikzpicture}[baseline=0.5cm,scale=0.33]		
			\draw(0,0)--(0,1);
			\draw(0,1)--(-1,2)--(-1,3);
			\draw(0,1)--(1,2)--(1,3);
			\node at (0,0) [anchor=north] {$c$};
			\node at (-1,3) [anchor=south] {$b$};
			\node at (1,3) [anchor=south] {$a$};
		\end{tikzpicture}
	\end{align}
where $a$, $b$, and $c$ represent particle types, or $F$-moves, representing the associativity rule for fusion processes, denoted as
	\begin{align}
		\begin{tikzpicture}[baseline=0.6cm,scale=0.4]
			\draw(0,0)--(0,1)--(-2,3);
			\draw(0,3)--(-1,2);
			\draw(2,3)--(0,1);
			\node at (-0.45,1.6) [anchor=north east] {$i$};
			\node at (0,0) [anchor=north] {$d$};
			\node at (2,3) [anchor=south] {$c$};
			\node at (0,3) [anchor=south] {$b$};
			\node at (-2,3) [anchor=south] {$a$};
		\end{tikzpicture}
		&\;\;=\;\;\sum_j[F^{abc}_d]_{ij}\cdot\;
		\begin{tikzpicture}[baseline=0.6cm,scale=0.4]		
			\draw(0,0)--(0,1)--(-2,3);
			\draw(0,3)--(1,2);
			\draw(2,3)--(0,1);
			\node at (0.42,1.63) [anchor=north west] {$j$};
			\node at (0,0) [anchor=north] {$d$};
			\node at (2,3) [anchor=south] {$c$};
			\node at (0,3) [anchor=south] {$b$};
			\node at (-2,3) [anchor=south] {$a$};
		\end{tikzpicture}
	\end{align}

These manipulations encode the data of the unitary modular tensor category, and can be used to represent the state of a system of anyons as a linear combination of fusion trees. For the Fibonacci anyons, the non-trivial $R$ and $F$ moves are given by
\begin{align}
	R_{\mathbb{I}}^{\tau\tau}&= \e^{\frac{-4\pi i}{5}}\qquad R_\tau^{\tau\tau}= \e^{\frac{3\pi i}{5}}\\
	F_{\tau}^{\tau\tau\tau} &= \begin{pmatrix}\varphi^{-1}&\varphi^{-\frac{1}{2}}\\\varphi^{-\frac{1}{2}}&-\varphi^{-1}\end{pmatrix} \,,
\end{align}
where in the last expression, $\varphi=\frac{1+\sqrt{5}}{2}$ is the golden ratio, and the matrix is given in a basis labelled $(\mathbb{I},\tau)$.

We use a phenomenological model of Fibonacci anyon dynamics which neglects any 
microscopic details of the system. 
This is consistent with the principles of topologically 
ordered systems and anyonic physics, where the key universal features describing the 
anyon model correspond to large length-scale physics, while the microscopic physics plays 
a less important (and non-universal) role. Effectively, we simulate a $(2+1)$-dimensional topological quantum field theory on a discrete space-time.
As such, we model the system simply as a 
periodic $L\times L$ square lattice $\Lambda$ of sites upon which sets of anyons can 
reside. Allowed anyon dynamics (pair-creation, braiding, and fusion) are considered to act 
locally on edges of $\Lambda$. For more details of an analogous model, see~\cite{Brell2013}.

@@

Our error-correction algorithm is based on a hard-decision renormalization group (RG) 
decoder~\cite{Bravyi2011}. 
The decoder proceeds by measuring the occupations of 
anyons at each site of the lattice, forming clusters of nearby anyons and fusing the anyons 
within each cluster, before iterating at linearly increasing length scales.
It terminates when the lattice 
is free of anyons (i.e.~we have returned to the codespace) or the clustering length scale exceeds the size of the lattice.
%the decoder performs a homologically nontrivial operation, thereby altering the codespace.
%\cggb{our simulation may terminate when the decoder performs a nontrivial operation, but here we're just describing the decoder, which can't know that.}
%\cggb{A few more details? What is our length schedule?} 
%\cggb{How does our decoder relate to other decoding schemes used in~\cite{Wootton2013,Brell2013,Hutter2014}?} 
Note that, as was found in Ref.~\cite{Brell2013}, we expect that our qualitative results may be reproduced by most alternative families of decoders, although it may not be clear in all cases how to extend these decoders to the non-abelian setting.
The advantage of using a hard-decision RG decoder is 
its simplicity and flexibility, and the fact that its clustering scheme is compatible with the structure in the noise processes that allows us to classically simulate them.

@@

Below the (bond) percolation threshold for (say) a 2D square lattice, we expect random sets of 
bonds to decompose into separate clusters~\footnote{We use the word cluster to refer both to groupings of nearby anyons as formed by the decoding algorithm and to connected components of a graph under percolation, since both of these usages are standard in the literature. The intended meaning will remain clear from context.} of average size $O(\log(n))$ and variance 
$O(1)$~\cite{Bazant2000}.
Each noise process in our model is associated with a (randomly distributed) edge, and so 
disconnected clusters correspond to sets of anyons that could not have interacted at any 
point in their history. Although normally anyons can interact by braiding without ever coming into contact with one another, in this case charge conservation implies that each distinct cluster must have trivial total charge, and so all such interactions are trivial.
This allows us to simulate the braiding processes within each cluster 
separately. In other words: the quantum state in the fusion space of all anyons factorizes into 
a tensor product over bond clusters, and we can compute each factor separately. Since each 
cluster has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. There are rare 
random processes that violate this reasoning, but processes such as these are suppressed 
exponentially in the lattice size $L$\cite{Grimmett1989}.

However, random noise processes are not the only dynamics that we need to consider. We 
must also consider the effect of the error-correction routine itself. This acts iteratively to fuse 
particles on increasing length scales. While this kind of fusion would typically merge clusters, 
forcing us to compute dynamics of larger and larger sets of anyons, large clusters are sparsely distributed 
(and thus unlikely to be merged), and in addition at each length scale the total number of 
anyons present is dramatically reduced by fusion, leading to a smaller number of anyons that 
must be simulated.

Of course, if we were to consider noise so strong that the clusters percolate over the entire lattice, we would no longer expect to be able to efficiently simulate the noise and recovery processes in the system. 
However, recall that logical errors in our system correspond to processes that act over a non-trivial loop of the torus. 
Our simulation remains efficient until the point that we start to create nontrivial loops around the torus, and our simulation begins to declare failure whenever non-trivial logical operations occur, meaning that we can simulate large lattice sizes in the successful error-correction (sub-percolated) regime, including up to $L=128$.

@@

\begin{figure}[th!]
\begin{center}
	\includegraphics[width=\columnwidth]{pic-syndrome.pdf}
\caption{Four equivalent representations of a state,
along with two syndrome observables marked with solid and dashed lines:
(a) two pairs are joined in (b).
Deform the curve straight to get (c),
then effect some
braid operations on the state so that (d) the two
observables are now represented on the curve. \cggb{I'm not totally clear on what I'm looking at here. Is this the diagram where we want to explain the whole simulation algorithm? Is the idea that we start with a), which is given by the set of noise processes that have happened, then we connect stuff up arbitrarily into b) to make some fusion tree. Then c) is what's happening after linearizing the picture? And d) is c) after some R and F moves so you go into the standard basis for the fusion tree? Are the red lines between c) and d) just denoting leaves with the same identity or do they have some more precise meaning wrt the braid moves that relate c) and d)?}}
\label{f:syndrome}
\end{center}
\end{figure}

\begin{figure}[th!]
\begin{center}
	\includegraphics[width=\columnwidth]{pic-decode.pdf}
\caption{The decoder works by maintaining a set of disjoint clusters (rooted trees). \cggb{Is this diagram where we want to explain the decoding algorithm? Is part a) round one of clustering and part b) round 2 of clustering? Do the arrow directions just denote the direction stuff goes when we try to fuse it all together or does it have some deeper meaning?}}
\label{f:decode}
\end{center}
\end{figure}

@@

We can guarantee that error-correction will succeed whenever noise does not percolate, but it is possible that percolated events may still result in no error. 
The connection between the percolation threshold and the error-correction threshold is not well understood in general~\cite{Hastings2014}, though it is clear that our threshold estimate will be a lower bound for the true threshold that may be found if all events (including those that have percolated) were simulated by an optimal decoder. 
However, calculations of such nontrivial operations suggest that all such processes will indeed result in a logical or leakage error.
As such it is likely that neglecting full simulation for such events does not significantly affect our observed threshold value.

@@

We have demonstrated classical simulation of successful error correction in a universal anyon model. 
Though we have chosen several properties of our model and simulation in a convenient way for simplicity, it seems highly unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}. 
In particular, although we have modeled our logical qubit as encoded in the global topological degrees of freedom of our system, we could have encoded it in the fusion space of several preferred $\tau$ anyons. 
This situation would be appropriate to model error-correction routines for topological quantum computation. 
Additionally, we expect our results to be stable to changes in details of the noise model and decoding algorithm.
